An Improved Method for Coupling Hydrodynamics with Reaction Networks and Nuclear Statistical Equilibrium

### 2021-04-24 simplified_sdc_intro/paper.tex
ome updates
update NSE algorithm

With SDC evolution, when we are in NSE, we need to do the advective
and reactive updates together.  With the tabulated NSE reaction
values, we get instantaneous values of the reaction sources, but the only
time derivative we have is for $Y_e$.  We will
use a basic predictor-corrector update:
\begin{equation}
\Uc^\star = \Uc^n + \Delta t \Adv{\Uc}^{n+1/2} + \Delta t \left [\Rb (\Uc) \right ]^{n+1/2}
\end{equation}
Calling the NSE table on the starting state gives us:
\begin{equation}
\nse{\rho^n, T^n, (Y_e)^n} \rightarrow \bar{A}^n, (X_k)^n, (B/A)^n, (dY_e/dt)^n
\end{equation}
To get the reactive source, we need to use the iteratively-lagged time-centered information
from $\Ic_q^{n+1/2,(k-1)}$.  We only need to update the internal energy and auxiliary data,
since together with the density, that is all that is needed for the equation of state to get the
updated temperature.    So our sources are:
\begin{equation}
R(\rho e) \approx \Ics_q(\rho e)
\end{equation}
and
\begin{equation}
R(\rho \alpha_l) \approx \rho^{n+1/2} \Ics_q(\alpha_l)
\end{equation}
where $\rho^{n+1/2} = (\rho^n + \rho^\star)/2$.

Since we have $(dY_e/dt)^n$ from the table, we replace the source for $Y_e$ in the above
$\Rb(\Uc^n)$ as: \MarginPar{it might be better if we had $\Ics_\Uc$}
\begin{equation}
R(\rho Y_e) = \rho^{n+1/2} (dY_e/dt)^n
\end{equation}
which gives an update for the electron fraction as:
\begin{equation}
(\rho Y_e)^\star = (\rho Y_e)^n + \Delta t \Advss{\rho Y_e}^{n+1/2} + \Delta t \rho^{n+1/2} (dY_e/dt)^n
\end{equation}
We can then get $\alpha_l^\star = (\rho \alpha_l)^\star/\rho^\star$.
From this prediction, we get $\rho^\star$, $\alpha_l^\star$, and
$e^\star$, which allows us to call the EOS and get an updated
temperature, $T^\star$. \MarginPar{Andy suggests time-centering $dY_e/dt$}
\begin{equation}
T^\star = T(\rho^\star, \alpha_l^\star, e^\star)
\end{equation}
We can then again call the NSE table:
\begin{equation}
\nse{\rho^\star, T^\star, (Y_e)^\star} \rightarrow \bar{A}^{n+1,(k)}, (X_k)^{n+1,(k)}, (B/A)^{n+1,(k)}, (dY_e/dt)
\end{equation}
where we use the outputs to define the new values of the composition variables.
Since the density and momenta don't have reactive sources, we just use the $\Uc^\star$ state
as their new values:
\begin{align}
\rho^{n+1,(k)} &= \rho^\star \\
(\rho u)^{n+1,(k)} &= (\rho u)^\star
\end{align}
We then compute the energy release as
\begin{equation}
       (\rho \Sdot)^{n+1/2} = \frac{\rho^{n+1,(k)} + \rho^n}{2}
             \left [ \left ( \frac{B}{A} \right )^{n+1,(k)} -
                     \left ( \frac{B}{A} \right )^n \right ] N_A \frac{1}{\Delta t}
\end{equation}

{\color{red}
Note I tried this first, but it really doesn't work.  I'd like to understand better:
\begin{equation}
       (\rho \Sdot)^{n+1/2} = \left [ \rho^{n+1,(k)} \left ( \frac{B}{A} \right )^{n+1,(k)} -
                            \rho^n \left ( \frac{B}{A} \right )^n \right ] N_A \frac{1}{\Delta }t
\end{equation}
}
and then do the final update of the total energy:
\begin{equation}
(\rho E)^{n+1,(k)} = (\rho E)^n + \Delta t \Advss{\rho E}^{n+1/2} + \Delta t (\rho \Sdot)^{n+1/2}
\end{equation}

@@

\begin{deluxetable}{lllllll}
\tablecaption{\label{table:react_convert_strang} Convergence ($L_1$ norm) for the reacting convergence problem using Strang splitting.}
\tablehead{\colhead{field} & \colhead{$\epsilon_{64 \rightarrow 128}$} & 
           \colhead{rate} & \colhead{$\epsilon_{128\rightarrow 256}$} & 
           \colhead{rate} & \colhead{$\epsilon_{256\rightarrow 512}$}}
\startdata
 $\rho$                      & $2.781 \times 10^{18}$  & 2.051  & $6.711 \times 10^{17}$  & 2.580  & $1.122 \times 10^{17}$  \\
 $\rho u$                    & $6.781 \times 10^{26}$  & 2.445  & $1.245 \times 10^{26}$  & 2.907  & $1.659 \times 10^{25}$  \\
 $\rho v$                    & $6.781 \times 10^{26}$  & 2.445  & $1.245 \times 10^{26}$  & 2.907  & $1.659 \times 10^{25}$  \\
 $\rho E$                    & $2.465 \times 10^{35}$  & 2.333  & $4.892 \times 10^{34}$  & 2.650  & $7.794 \times 10^{33}$  \\
 $\rho e$                    & $2.268 \times 10^{35}$  & 2.298  & $4.610 \times 10^{34}$  & 2.722  & $6.988 \times 10^{33}$  \\
 $T$                         & $2.248 \times 10^{21}$  & 1.682  & $7.003 \times 10^{20}$  & 2.439  & $1.291 \times 10^{20}$  \\
 $\rho X(\isotm{He}{4})$     & $2.862 \times 10^{18}$  & 2.027  & $7.023 \times 10^{17}$  & 2.554  & $1.196 \times 10^{17}$  \\
 $\rho X(\isotm{C}{12})$     & $1.717 \times 10^{17}$  & 1.945  & $4.460 \times 10^{16}$  & 2.194  & $9.745 \times 10^{15}$  \\
 $\rho X(\isotm{O}{16})$     & $1.718 \times 10^{14}$  & 1.648  & $5.482 \times 10^{13}$  & 1.898  & $1.471 \times 10^{13}$  \\
 $\rho X(\isotm{Fe}{56})$    & $2.781 \times 10^{8}$   & 2.051  & $6.711 \times 10^{7}$   & 2.580  & $1.122 \times 10^{7}$   \\
\enddata
\end{deluxetable}

@@

\begin{deluxetable}{lllllll}
\tablecaption{\label{table:react_convert_strang} Convergence ($L_1$ norm) for the reacting convergence problem using SDC integration (2 iterations).}
\tablehead{\colhead{field} & \colhead{$\epsilon_{64 \rightarrow 128}$} & 
           \colhead{rate} & \colhead{$\epsilon_{128\rightarrow 256}$} & 
           \colhead{rate} & \colhead{$\epsilon_{256\rightarrow 512}$}}
\startdata
 $\rho$                      & $2.794 \times 10^{18}$  & 2.047  & $6.760 \times 10^{17}$  & 2.563  & $1.144 \times 10^{17}$  \\
 $\rho u$                    & $6.796 \times 10^{26}$  & 2.450  & $1.243 \times 10^{26}$  & 2.898  & $1.669 \times 10^{25}$  \\
 $\rho v$                    & $6.796 \times 10^{26}$  & 2.450  & $1.243 \times 10^{26}$  & 2.898  & $1.669 \times 10^{25}$  \\
 $\rho E$                    & $2.450 \times 10^{35}$  & 2.357  & $4.783 \times 10^{34}$  & 2.743  & $7.144 \times 10^{33}$  \\
 $\rho e$                    & $2.261 \times 10^{35}$  & 2.325  & $4.513 \times 10^{34}$  & 2.821  & $6.385 \times 10^{33}$  \\
 $T$                         & $2.236 \times 10^{21}$  & 1.690  & $6.929 \times 10^{20}$  & 2.473  & $1.248 \times 10^{20}$  \\
 $\rho X(\isotm{He}{4})$     & $2.877 \times 10^{18}$  & 2.023  & $7.078 \times 10^{17}$  & 2.536  & $1.220 \times 10^{17}$  \\
 $\rho X(\isotm{C}{12})$     & $1.697 \times 10^{17}$  & 1.947  & $4.402 \times 10^{16}$  & 2.222  & $9.436 \times 10^{15}$  \\
 $\rho X(\isotm{O}{16})$     & $1.688 \times 10^{14}$  & 1.658  & $5.349 \times 10^{13}$  & 1.950  & $1.385 \times 10^{13}$  \\
 $\rho X(\isotm{Fe}{56})$    & $2.794 \times 10^{8}$   & 2.047  & $6.760 \times 10^{7}$   & 2.563  & $1.144 \times 10^{7}$   \\
\enddata
\end{deluxetable}

@@

\begin{deluxetable}{lllllll}
\tablecaption{\label{table:nse_strang_methodII} Convergence ($L_1$ norm) for the NSE convergence
problem using Strang splitting.}
\tablehead{\colhead{field} & \colhead{$\epsilon_{64 \rightarrow 128}$} & 
           \colhead{rate} & \colhead{$\epsilon_{128\rightarrow 256}$} & 
           \colhead{rate} & \colhead{$\epsilon_{256\rightarrow 512}$}}
\startdata
 $\rho$                      & $4.522 \times 10^{19}$  & 1.659  & $1.432 \times 10^{19}$  & 1.542  & $4.917 \times 10^{18}$  \\
 $\rho u$                    & $1.883 \times 10^{28}$  & 1.681  & $5.873 \times 10^{27}$  & 1.524  & $2.042 \times 10^{27}$  \\
 $\rho v$                    & $1.883 \times 10^{28}$  & 1.681  & $5.873 \times 10^{27}$  & 1.524  & $2.042 \times 10^{27}$  \\
 $\rho E$                    & $5.933 \times 10^{37}$  & 1.613  & $1.940 \times 10^{37}$  & 1.411  & $7.293 \times 10^{36}$  \\
 $\rho e$                    & $5.931 \times 10^{37}$  & 1.613  & $1.939 \times 10^{37}$  & 1.411  & $7.291 \times 10^{36}$  \\
 $T$                         & $9.885 \times 10^{20}$  & 1.207  & $4.281 \times 10^{20}$  & 1.058  & $2.057 \times 10^{20}$  \\
 $\rho X(\isotm{He}{4})$     & $5.086 \times 10^{17}$  & 1.430  & $1.887 \times 10^{17}$  & 1.187  & $8.288 \times 10^{16}$  \\
 $\rho X(\isotm{C}{12})$     & $1.585 \times 10^{12}$  & 1.829  & $4.462 \times 10^{11}$  & 1.433  & $1.652 \times 10^{11}$  \\
 $\rho X(\isotm{O}{16})$     & $8.060 \times 10^{12}$  & 1.706  & $2.470 \times 10^{12}$  & 1.347  & $9.710 \times 10^{11}$  \\
 $\rho X(\isotm{Cr}{48})$    & $1.149 \times 10^{19}$  & 1.400  & $4.353 \times 10^{18}$  & 1.258  & $1.820 \times 10^{18}$  \\
 $\rho X(\isotm{Fe}{52})$    & $9.018 \times 10^{19}$  & 1.173  & $4.001 \times 10^{19}$  & 1.127  & $1.832 \times 10^{19}$  \\
 $\rho X(\isotm{Fe}{54})$    & $5.036 \times 10^{20}$  & 1.731  & $1.517 \times 10^{20}$  & 1.727  & $4.582 \times 10^{19}$  \\
 $\rho X(\isotm{Ni}{56})$    & $5.686 \times 10^{20}$  & 1.622  & $1.847 \times 10^{20}$  & 1.563  & $6.252 \times 10^{19}$  \\
 $\rho Y_e$                  & $2.379 \times 10^{19}$  & 1.678  & $7.431 \times 10^{18}$  & 1.578  & $2.489 \times 10^{18}$  \\
 $\rho \bar{A}$              & $5.141 \times 10^{21}$  & 1.230  & $2.191 \times 10^{21}$  & 1.087  & $1.032 \times 10^{21}$  \\
 $\rho (B/A)$                & $4.149 \times 10^{20}$  & 1.693  & $1.283 \times 10^{20}$  & 1.562  & $4.345 \times 10^{19}$  \\
\enddata
\end{deluxetable}

\begin{deluxetable}{lllllll}
\tablecaption{\label{table:nse_strang_methodII} Convergence ($L_1$ norm) for the NSE convergence
problem using the simplified-SDC algorithm.}
\tablehead{\colhead{field} & \colhead{$\epsilon_{64 \rightarrow 128}$} & 
           \colhead{rate} & \colhead{$\epsilon_{128\rightarrow 256}$} & 
           \colhead{rate} & \colhead{$\epsilon_{256\rightarrow 512}$}}
\startdata
 $\rho$                      & $4.558 \times 10^{19}$  & 1.633  & $1.470 \times 10^{19}$  & 1.578  & $4.923 \times 10^{18}$  \\
 $\rho u$                    & $1.945 \times 10^{28}$  & 1.648  & $6.208 \times 10^{27}$  & 1.513  & $2.176 \times 10^{27}$  \\
 $\rho v$                    & $1.945 \times 10^{28}$  & 1.648  & $6.208 \times 10^{27}$  & 1.513  & $2.176 \times 10^{27}$  \\
 $\rho E$                    & $5.710 \times 10^{37}$  & 1.620  & $1.857 \times 10^{37}$  & 1.552  & $6.333 \times 10^{36}$  \\
 $\rho e$                    & $5.708 \times 10^{37}$  & 1.620  & $1.857 \times 10^{37}$  & 1.553  & $6.331 \times 10^{36}$  \\
 $T$                         & $5.873 \times 10^{20}$  & 1.621  & $1.910 \times 10^{20}$  & 1.494  & $6.779 \times 10^{19}$  \\
 $\rho X(\isotm{He}{4})$     & $2.453 \times 10^{17}$  & 1.835  & $6.876 \times 10^{16}$  & 1.657  & $2.181 \times 10^{16}$  \\
 $\rho X(\isotm{C}{12})$     & $1.130 \times 10^{12}$  & 1.846  & $3.145 \times 10^{11}$  & 1.678  & $9.831 \times 10^{10}$  \\
 $\rho X(\isotm{O}{16})$     & $5.339 \times 10^{12}$  & 1.830  & $1.502 \times 10^{12}$  & 1.667  & $4.730 \times 10^{11}$  \\
 $\rho X(\isotm{Cr}{48})$    & $6.880 \times 10^{18}$  & 1.791  & $1.988 \times 10^{18}$  & 1.601  & $6.554 \times 10^{17}$  \\
 $\rho X(\isotm{Fe}{52})$    & $3.470 \times 10^{19}$  & 1.606  & $1.140 \times 10^{19}$  & 1.608  & $3.740 \times 10^{18}$  \\
 $\rho X(\isotm{Fe}{54})$    & $4.766 \times 10^{20}$  & 1.764  & $1.403 \times 10^{20}$  & 1.777  & $4.093 \times 10^{19}$  \\
 $\rho X(\isotm{Ni}{56})$    & $4.835 \times 10^{20}$  & 1.781  & $1.407 \times 10^{20}$  & 1.788  & $4.075 \times 10^{19}$  \\
 $\rho Y_e$                  & $2.370 \times 10^{19}$  & 1.644  & $7.582 \times 10^{18}$  & 1.580  & $2.536 \times 10^{18}$  \\
 $\rho \bar{A}$              & $4.061 \times 10^{21}$  & 1.678  & $1.270 \times 10^{21}$  & 1.675  & $3.975 \times 10^{20}$  \\
 $\rho (B/A)$                & $4.224 \times 10^{20}$  & 1.664  & $1.333 \times 10^{20}$  & 1.602  & $4.391 \times 10^{19}$  \\
\enddata
\end{deluxetable}

>>>>

With SDC evolution, when we are in NSE, we need to do the advective
and reactive updates together.  We want to compute:
\begin{equation}
\Uc^{n+1,(k)} = \Uc^n + \Delta t \Adv{\Uc}^{n+1/2,(k)} + \Delta t \left [\Rb (\Uc) \right ]^{n+1/2,(k)}
\end{equation}
For density and momentum, we can do this update already, since there
are no reactive sources.  That gives us $\rho^{n+1,(k)}$ and $(\rho
\Ub)^{n+1,(k)}$.  For the other quantities, the NSE table gives only the
instantaneous values. aside from $Y_e$.  We therefore do an iterative
update.

Calling the NSE table on the starting state gives us:
\begin{equation}
\nse{\rho^n, T^n, (Y_e)^n} \rightarrow \bar{A}^n, (X_k)^n, (B/A)^n, (dY_e/dt)^n
\end{equation}
We now compute a first approximation to the reactive source:
\begin{align}
R^{(0)}(\rho e) &= 0 \\
R^{(0)}(\rho Y_e) &= \rho^n (dY_e/dt)^n \\
R^{(0)}(\rho \bar{A}) &= 0
\end{align}

Now we iterate $\xi = 0, \ldots N-1$, doing the following:

\begin{itemize}
\item Update the energy as:
   \begin{equation}
     (\rho e)^{n+1,(\xi)} = (\rho e)^n + \Delta t \Advss{\rho e}^{n+1/2,(k)} + \Delta t R^{(\xi)}(\rho e)
   \end{equation}

\item Update the auxiliary data as:
   \begin{equation}
     (\rho \alpha_l)^{n+1,(\xi)} = (\rho \alpha_l)^n + \Delta t \Advss{\rho \alpha_l}^{n+1/2,(k)} + \Delta t R^{(\xi)}(\rho \alpha_l)
   \end{equation}

\item Compute the updated temperature, $T^{n+1,(k)}$ as
  \begin{equation}
    T^{n+1,(\xi)} = T(\rho^{n+1,(k)},  \alpha^{n+1,(\xi)},  e^{n+1,(\xi)})
  \end{equation}
  where $\alpha^{n+1,(\xi)} = (\rho  \alpha)^{n+1,(\xi)} / \rho^{n+1,(k)}$ and $e^{n+1,(\xi)} = (\rho e)^{n+1,(\xi)} / \rho^{n+1,(k)}$.

\item Call the NSE table to get the new NSE state
  \begin{equation}
    \nse{\rho^{n+1,(k)}, T^{n+1,(\xi)}, (Y_e)^{n+1,(\xi)}} \rightarrow \bar{A}^{n+1,(\xi)}, (X_k)^{n+1,(\xi)}, (B/A)^{n+1,(\xi)}, (dY_e/dt)^{n+1,(\xi)}
  \end{equation}

\item Recompute the reactive source terms for the next iteration.

  The energy generation rate is found as:
  \begin{equation}
    (\rho \Sdot)^{n+1/2,(\xi)} = \frac{\rho^{n+1,(k)} + \rho^n}{2}
    \left [ \left ( \frac{B}{A} \right )^{n+1,(\xi)} -
      \left ( \frac{B}{A} \right )^n \right ] N_A \frac{1}{\Delta t}
  \end{equation}
  and our new auxiliary sources are:
\begin{align}
R^{(\xi+1)}(\rho e) &= (\rho \Sdot)^{n+1/2,(\xi)} \\
R^{(\xi+1)}(\rho Y_e) &= \frac{\rho^{n+1,(k)} + \rho^n}{2} \frac{1}{2} \left [ \left (\frac{dY_e}{dt} \right )^n + \left (\frac{dY_e}{dt} \right )^{n+1,(\xi)} \right ] \\
R^{(\xi+1)}(\rho \bar{A}) &= \frac{\rho^{n+1,(k)} + \rho^n}{2} \frac{1}{\Delta t} \left [ \bar{A}^{n+1,(\xi)} - \frac{(\rho \bar{A})^n}{\rho^n} \right ]
\end{align}

With the iteration complete, we can do the final update of the total energy using last iterations prediction of the source (for iteration $N$):
\begin{equation}
(\rho E)^{n+1,(k)} = (\rho E)^n + \Delta t \Advss{\rho E}^{n+1/2} + \Delta t (\rho \Sdot)^{n+1/2,(N)}
\end{equation}
and we take the values of the auxiliary state and mass fractions from the last call to the NSE table:
\begin{align}
(\rho Y_e)^{n+1,(k)} &= \rho^{n+1,(k)} (Y_e)^{n+1,(N-1)} \\
(\rho \bar{A})^{n+1,(k)} &= \rho^{n+1,(k)} (\bar{A})^{n+1,(N-1)} \\
(\rho (B/A))^{n+1,(k)} &= \rho^{n+1,(k)} (B/A)^{n+1,(N-1)} \\
(\rho Y_e)^{n+1,(k)} &= \rho^{n+1,(k)} (X_k)^{n+1,(N-1)}
\end{align}

We note that this update is not fully second order, however, the
treatment of $Y_e$ is, and we expect that to have the dominant effect
in the thermodynamic evolution through NSE.

@@

\begin{deluxetable}{lllllll}
\tablecaption{\label{table:react_convert_strang} Convergence ($L_1$ norm) for the reacting convergence problem using Strang splitting.}
\tablehead{\colhead{field} & \colhead{$\epsilon_{64 \rightarrow 128}$} & 
           \colhead{rate} & \colhead{$\epsilon_{128\rightarrow 256}$} & 
           \colhead{rate} & \colhead{$\epsilon_{256\rightarrow 512}$}}
\startdata
 $\rho$                      & $2.794 \times 10^{18}$  & 2.044  & $6.777 \times 10^{17}$  & 2.554  & $1.154 \times 10^{17}$  \\
 $\rho u$                    & $6.796 \times 10^{26}$  & 2.448  & $1.245 \times 10^{26}$  & 2.889  & $1.681 \times 10^{25}$  \\
 $\rho v$                    & $6.796 \times 10^{26}$  & 2.448  & $1.245 \times 10^{26}$  & 2.889  & $1.681 \times 10^{25}$  \\
 $\rho E$                    & $2.451 \times 10^{35}$  & 2.351  & $4.803 \times 10^{34}$  & 2.742  & $7.179 \times 10^{33}$  \\
 $\rho e$                    & $2.261 \times 10^{35}$  & 2.320  & $4.526 \times 10^{34}$  & 2.821  & $6.403 \times 10^{33}$  \\
 $T$                         & $2.237 \times 10^{21}$  & 1.691  & $6.927 \times 10^{20}$  & 2.482  & $1.240 \times 10^{20}$  \\
 $\rho X(\isotm{He}{4})$     & $2.878 \times 10^{18}$  & 2.020  & $7.096 \times 10^{17}$  & 2.529  & $1.229 \times 10^{17}$  \\
 $\rho X(\isotm{C}{12})$     & $1.698 \times 10^{17}$  & 1.950  & $4.393 \times 10^{16}$  & 2.232  & $9.353 \times 10^{15}$  \\
 $\rho X(\isotm{O}{16})$     & $1.687 \times 10^{14}$  & 1.660  & $5.338 \times 10^{13}$  & 1.957  & $1.375 \times 10^{13}$  \\
 $\rho X(\isotm{Fe}{56})$    & $2.794 \times 10^{8}$   & 2.044  & $6.777 \times 10^{7}$   & 2.554  & $1.154 \times 10^{7}$   \\
\enddata
\end{deluxetable}

@@

\begin{deluxetable}{lllllll}
\tablecaption{\label{table:react_convert_strang} Convergence ($L_1$ norm) for the reacting convergence problem using SDC integration (2 iterations).}
\tablehead{\colhead{field} & \colhead{$\epsilon_{64 \rightarrow 128}$} & 
           \colhead{rate} & \colhead{$\epsilon_{128\rightarrow 256}$} & 
           \colhead{rate} & \colhead{$\epsilon_{256\rightarrow 512}$}}
\startdata
 $\rho$                      & $2.795 \times 10^{18}$  & 2.044  & $6.777 \times 10^{17}$  & 2.554  & $1.154 \times 10^{17}$  \\
 $\rho u$                    & $6.798 \times 10^{26}$  & 2.449  & $1.245 \times 10^{26}$  & 2.889  & $1.680 \times 10^{25}$  \\
 $\rho v$                    & $6.798 \times 10^{26}$  & 2.449  & $1.245 \times 10^{26}$  & 2.889  & $1.680 \times 10^{25}$  \\
 $\rho E$                    & $2.452 \times 10^{35}$  & 2.352  & $4.804 \times 10^{34}$  & 2.742  & $7.179 \times 10^{33}$  \\
 $\rho e$                    & $2.262 \times 10^{35}$  & 2.321  & $4.527 \times 10^{34}$  & 2.822  & $6.404 \times 10^{33}$  \\
 $T$                         & $2.236 \times 10^{21}$  & 1.691  & $6.927 \times 10^{20}$  & 2.481  & $1.240 \times 10^{20}$  \\
 $\rho X(\isotm{He}{4})$     & $2.879 \times 10^{18}$  & 2.020  & $7.096 \times 10^{17}$  & 2.529  & $1.229 \times 10^{17}$  \\
 $\rho X(\isotm{C}{12})$     & $1.697 \times 10^{17}$  & 1.950  & $4.393 \times 10^{16}$  & 2.231  & $9.357 \times 10^{15}$  \\
 $\rho X(\isotm{O}{16})$     & $1.686 \times 10^{14}$  & 1.659  & $5.338 \times 10^{13}$  & 1.957  & $1.375 \times 10^{13}$  \\
 $\rho X(\isotm{Fe}{56})$    & $2.795 \times 10^{8}$   & 2.044  & $6.777 \times 10^{7}$   & 2.554  & $1.154 \times 10^{7}$   \\
\enddata
\end{deluxetable}

@@

\begin{deluxetable}{lllllll}
\tablecaption{\label{table:nse_strang_methodII} Convergence ($L_1$ norm) for the NSE convergence
problem using Strang splitting.}
\tablehead{\colhead{field} & \colhead{$\epsilon_{64 \rightarrow 128}$} & 
           \colhead{rate} & \colhead{$\epsilon_{128\rightarrow 256}$} & 
           \colhead{rate} & \colhead{$\epsilon_{256\rightarrow 512}$}}
\startdata
 $\rho$                      & $4.522 \times 10^{19}$  & 1.659  & $1.432 \times 10^{19}$  & 1.542  & $4.917 \times 10^{18}$  \\
 $\rho u$                    & $1.883 \times 10^{28}$  & 1.681  & $5.873 \times 10^{27}$  & 1.524  & $2.042 \times 10^{27}$  \\
 $\rho v$                    & $1.883 \times 10^{28}$  & 1.681  & $5.873 \times 10^{27}$  & 1.524  & $2.042 \times 10^{27}$  \\
 $\rho E$                    & $5.933 \times 10^{37}$  & 1.613  & $1.940 \times 10^{37}$  & 1.411  & $7.293 \times 10^{36}$  \\
 $\rho e$                    & $5.931 \times 10^{37}$  & 1.613  & $1.939 \times 10^{37}$  & 1.411  & $7.291 \times 10^{36}$  \\
 $T$                         & $9.885 \times 10^{20}$  & 1.207  & $4.281 \times 10^{20}$  & 1.058  & $2.057 \times 10^{20}$  \\
 $\rho X(\isotm{H}{1})$      & $4.522 \times 10^{-11}$ & 1.659  & $1.432 \times 10^{-11}$ & 1.542  & $4.917 \times 10^{-12}$ \\
 $\rho X(\isotm{He}{4})$     & $5.086 \times 10^{17}$  & 1.430  & $1.887 \times 10^{17}$  & 1.187  & $8.288 \times 10^{16}$  \\
 $\rho X(\isotm{C}{12})$     & $1.585 \times 10^{12}$  & 1.829  & $4.462 \times 10^{11}$  & 1.433  & $1.652 \times 10^{11}$  \\
 $\rho X(\isotm{O}{16})$     & $8.060 \times 10^{12}$  & 1.706  & $2.470 \times 10^{12}$  & 1.347  & $9.710 \times 10^{11}$  \\
 $\rho X(\isotm{Cr}{48})$    & $1.149 \times 10^{19}$  & 1.400  & $4.353 \times 10^{18}$  & 1.258  & $1.820 \times 10^{18}$  \\
 $\rho X(\isotm{Fe}{52})$    & $9.018 \times 10^{19}$  & 1.173  & $4.001 \times 10^{19}$  & 1.127  & $1.832 \times 10^{19}$  \\
 $\rho X(\isotm{Fe}{54})$    & $5.036 \times 10^{20}$  & 1.731  & $1.517 \times 10^{20}$  & 1.727  & $4.582 \times 10^{19}$  \\
 $\rho X(\isotm{Ni}{56})$    & $5.686 \times 10^{20}$  & 1.622  & $1.847 \times 10^{20}$  & 1.563  & $6.252 \times 10^{19}$  \\
 $\rho Y_e$                  & $2.379 \times 10^{19}$  & 1.678  & $7.431 \times 10^{18}$  & 1.578  & $2.489 \times 10^{18}$  \\
 $\rho \bar{A}$              & $5.141 \times 10^{21}$  & 1.230  & $2.191 \times 10^{21}$  & 1.087  & $1.032 \times 10^{21}$  \\
 $\rho (B/A)$                & $4.149 \times 10^{20}$  & 1.693  & $1.283 \times 10^{20}$  & 1.562  & $4.345 \times 10^{19}$  \\
\enddata
\end{deluxetable}

\begin{deluxetable}{lllllll}
\tablecaption{\label{table:nse_strang_methodII} Convergence ($L_1$ norm) for the NSE convergence
problem using the simplified-SDC algorithm.}
\tablehead{\colhead{field} & \colhead{$\epsilon_{64 \rightarrow 128}$} & 
           \colhead{rate} & \colhead{$\epsilon_{128\rightarrow 256}$} & 
           \colhead{rate} & \colhead{$\epsilon_{256\rightarrow 512}$}}
\startdata
 $\rho$                      & $4.558 \times 10^{19}$  & 1.633  & $1.470 \times 10^{19}$  & 1.578  & $4.923 \times 10^{18}$  \\
 $\rho u$                    & $1.945 \times 10^{28}$  & 1.648  & $6.208 \times 10^{27}$  & 1.513  & $2.176 \times 10^{27}$  \\
 $\rho v$                    & $1.945 \times 10^{28}$  & 1.648  & $6.208 \times 10^{27}$  & 1.513  & $2.176 \times 10^{27}$  \\
 $\rho E$                    & $5.710 \times 10^{37}$  & 1.620  & $1.857 \times 10^{37}$  & 1.552  & $6.333 \times 10^{36}$  \\
 $\rho e$                    & $5.708 \times 10^{37}$  & 1.620  & $1.857 \times 10^{37}$  & 1.553  & $6.331 \times 10^{36}$  \\
 $T$                         & $5.873 \times 10^{20}$  & 1.621  & $1.910 \times 10^{20}$  & 1.494  & $6.779 \times 10^{19}$  \\
 $\rho X(\isotm{H}{1})$      & $4.558 \times 10^{-11}$ & 1.633  & $1.470 \times 10^{-11}$ & 1.578  & $4.923 \times 10^{-12}$ \\
 $\rho X(\isotm{He}{4})$     & $2.453 \times 10^{17}$  & 1.835  & $6.876 \times 10^{16}$  & 1.657  & $2.181 \times 10^{16}$  \\
 $\rho X(\isotm{C}{12})$     & $1.130 \times 10^{12}$  & 1.846  & $3.145 \times 10^{11}$  & 1.678  & $9.831 \times 10^{10}$  \\
 $\rho X(\isotm{O}{16})$     & $5.339 \times 10^{12}$  & 1.830  & $1.502 \times 10^{12}$  & 1.667  & $4.730 \times 10^{11}$  \\
 $\rho X(\isotm{Cr}{48})$    & $6.880 \times 10^{18}$  & 1.791  & $1.988 \times 10^{18}$  & 1.601  & $6.554 \times 10^{17}$  \\
 $\rho X(\isotm{Fe}{52})$    & $3.470 \times 10^{19}$  & 1.606  & $1.140 \times 10^{19}$  & 1.608  & $3.740 \times 10^{18}$  \\
 $\rho X(\isotm{Fe}{54})$    & $4.766 \times 10^{20}$  & 1.764  & $1.403 \times 10^{20}$  & 1.777  & $4.093 \times 10^{19}$  \\
 $\rho X(\isotm{Ni}{56})$    & $4.835 \times 10^{20}$  & 1.781  & $1.407 \times 10^{20}$  & 1.788  & $4.075 \times 10^{19}$  \\
 $\rho Y_e$                  & $2.370 \times 10^{19}$  & 1.644  & $7.582 \times 10^{18}$  & 1.580  & $2.536 \times 10^{18}$  \\
 $\rho \bar{A}$              & $4.061 \times 10^{21}$  & 1.678  & $1.270 \times 10^{21}$  & 1.675  & $3.975 \times 10^{20}$  \\
 $\rho (B/A)$                & $4.224 \times 10^{20}$  & 1.664  & $1.333 \times 10^{20}$  & 1.602  & $4.391 \times 10^{19}$  \\
\enddata
\end{deluxetable}
